API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
R2 score => coefficient of determination

Optionally, the model selection algorithms
also take a cross-validation scheme and a score function.  \sklearn provides
various such cross-validation schemes, including $k$-fold (default),
stratified $k$-fold and leave-one-out.
The score function used by default is the estimator's \texttt{score} method,
but the library provides a variety of
alternatives that the user can choose from,
including accuracy, AUC and $F_1$ score for classification,
$R^2$ score and mean squared error for regression.

>>>>

Optionally, the model selection algorithms
also take a cross-validation scheme and a score function.  \sklearn provides
various such cross-validation schemes, including $k$-fold (default),
stratified $k$-fold and leave-one-out.
The score function used by default is the estimator's \texttt{score} method,
but the library provides a variety of
alternatives that the user can choose from,
including accuracy, AUC and $F_1$ score for classification,
coefficient of determination and mean squared error for regression.
